The symmetry of partner modelling

### 2016-02-04 mutual-modeling.tex
Changed title
Updated abstract

\title{Mutual Modelling}

@@

\begin{abstract}
    Collaborative learning has something to do with building a shared
    understanding of the situation at hand. Yet, the psycholinguistics mechanisms
    at work while establishing common grounds are complex and certainly involve
    modelling what the partner knows/wants/intends at a given time.

    Building on a set of five independent studies that where conducted over
    several years, we propose in this article a simple model of the mechanisms
    of mutual modelling. It integrates several concepts related to the classical
    idea of grounding, and we apply it as an operational tool to
    analyse the interplay of learning and mutual modelling in the five studies.

    We come up with mixed experimental results that evidence the dual nature of
    mutual modelling: a individual meta-cognitive aptitude that co-exists with
    modelling elicited and fostered by social interactions.

>>>>

\title{The symmetry of partner modelling}

@@

\begin{abstract}
    Collaborative learning has often been associated to the construction of  a shared   understanding of the situation at hand. The psycholinguistics mechanisms
    at work while establishing common grounds are the object of scientific controversy. We postulate that collaborative tasks require some level of mutual 
    modeling, i.e. that each partner needs some model of what the other partners know/want/intend at a given time.  We use the term 'some model' to stress the fact that this model is not necessarily details or complete, but that we acquire some representations of the persons we interact with. The question we address is: 
Does the quality of the partner model depend upon the modeler's ability to represent his or her partner, upon the modelee's ability to make his state clear to the modeler or upon the quality of their interactions? We address this question by analyzing differences between the  accuracy of the models built by different team members. We therefore report 5 experiments on collaborative problem solving or collaborative learning that vary in terms of tasks (how important it is to build an accurate model) and settings (how difficult it is to build an accurate model). In 4 studies, the accuracy of the model that A built about B was correlated with the accuracy of the model that B built about A,  which seems to imply that the quality of interactions matters more than individual abilities when building mutual models.  However, these finding do not discard the fact individual abilities also  participate in the quality of modellng process .
